%\documentclass[submission,copyright,creativecommons]{eptcs}
\documentclass[submission]{eptcs}
%\documentclass[adraft]{eptcs}
%\documentclass[preliminary]{eptcs}
\providecommand{\event}{} % Name of the event you are submitting to
%\usepackage{breakurl}             % Not needed if you use pdflatex only.

%definitions
\input{head_pc}
\RequirePackage[normalem]{ulem}
\RequirePackage{color}\definecolor{RED}{rgb}{1,0,0}\definecolor{BLUE}{rgb}{0,0,1}
\providecommand{\DIFadd}[1]{{\protect\color{blue}\uwave{#1}}}
\providecommand{\DIFdel}[1]{{\protect\color{red}\sout{#1}}}
%DIF SAFE PREAMBLE
\providecommand{\DIFaddbegin}{}
\providecommand{\DIFaddend}{}
\providecommand{\DIFdelbegin}{}
\providecommand{\DIFdelend}{}
%DIF FLOATSAFE PREAMBLE
\providecommand{\DIFaddFL}[1]{\DIFadd{#1}}
\providecommand{\DIFdelFL}[1]{\DIFdel{#1}}
\providecommand{\DIFaddbeginFL}{}
\providecommand{\DIFaddendFL}{}
\providecommand{\DIFdelbeginFL}{}
\providecommand{\DIFdelendFL}{}

%
%\usepackage{etoolbox} %moved to head_pc.tex
%\newtoggle{appendixing} % whether to include appendices
%\toggletrue{appendixing}
%\togglefalse{appendixing}
%\iftoggle{appendixing}{%
  % using appendixing
%}{%
  % no appendixing
%}


%\title{Interpreting Name-passing with Abstraction-passing}
%\title{A New Encoding of Name-passing with Process-passing}
%\title{Parameterizing Higher-order Processes over Names and Processes}
%\title{Higher-order Processes with Parameterization over Names and Processes}
\title{Parameterizing Higher-order Processes on Names and Processes}
\author{Xian Xu
%\thanks{The paper is an expanded version of the work presented at EXPRESS/SOS 2016, EPTCS 8704: 78-92, 2016. }
\thanks{A preliminary version of this work was presented at EXPRESS/SOS 2016. %Comparatively, 
This paper extends that version with full-fledged proofs and more (refined) discussions (more than half new materials), and moreover, the detailed analysis of a variant encoding of interest. This encoding, mentioned only as a further direction in the preliminary version, is given thorough examination in this work.}
\thanks{This work has been supported by project ANR 12IS02001 PACE and NSF of China (61261130589, 61472239, 61572318).}
\institute{East China University of Science and Technology, Shanghai, China (200237)}
\email{xuxian@ecust.edu.cn}
%\and
%Qiang Yin \quad\qquad Huan Long
%\institute{Shanghai Jiao Tong University, China}
%\email{\quad yinqiang.sjtu@gmail.com \quad\qquad longhuan@sjtu.edu.cn}
}
%%\def\titlerunning{On the Computation Power of Name Parameterization in Higher-order Processes}
%\def\titlerunning{Higher-order Processes with Parameterization}
\def\titlerunning{}
%%\def\authorrunning{Xian Xu, Qiang Yin \& Huan Long}
%\def\authorrunning{Xian Xu}
\def\authorrunning{}

\begin{document}
\maketitle

%\oo{TODO : make it a journal paper.
%\begin{itemize}
%\item[DONE] add all the skipped/brief/missing proofs, e.g., Lemma \ref{l:syn-pro-encoding}, Theorem \ref{factor-bigd-smalld} and its preparing lemmas (see ICE2013 paper \cite{Xu13});
%\item[DONE] add the detailed discussion for normal characterization for context bisimulation in $\HOPid$ (see ICE 2013 paper \cite{Xu13});
%\item[DONE] add the discussion of the variant encoding in Section \ref{s:conclusion};
%\item adjust and improve the whole paper to be consistent (including presentation): 
%\begin{itemize}
%\item[DONE] start from Section \ref{s:conclusion}; %, now at Section \ref{smalld-charac}; 
%\item[DONE] %[\bc{to continue from Section 2}] 
%then from the beginning, noticing the result on the variant encoding; 
%\end{itemize}
%\item[DONE] spell-check and maybe more checks;
%\item send.
%\end{itemize}
%}

%\bc{TODO :\rc{make it a (workshop) paper} (technical stuff nearly ok now); } %\bc{$\checkmark$}}
%\begin{itemize}
%\item introduction.  \bc{$\checkmark$}
%\item definition.  \bc{$\checkmark$}
%\item conclusion.  \bc{$\checkmark$}
%\item tidy up (remove the tiny comments by redefining ``$\backslash$tdup").  \bc{$\checkmark$}
%\item page limit and more readable (\rc{flow})  \,\&\,  remove colors and nts %\bc{$\checkmark$}
%\item \greycolor{Words: facilitate, demonstrate, be dedicated to, }
%\end{itemize}
%\sep
%\vspace*{-.5cm}
\nts{
\bc{TODO :make it a journal paper (with easy-recognizing extension); } %\bc{$\checkmark$}}
\begin{itemize}
\item move the variant encoding into a separate section. give full discussion there. \bc{$\checkmark$}
\item to the previous point, adjust the related part in conclusion/introduction.  \bc{$\checkmark$}
\item revise using the review (those useful part; discard others).  \bc{$\checkmark$}
\item READ through (further factor and tidy up, emphasizing the contribution and difference from the workshop paper in the introduction, e.g., copy sth from the cover letter). \bc{$\checkmark$}
\item try another journal (maybe avoid elsevier); to be done in ``sourcecode\_long\_svjour\_v2.1''. \bc{$\checkmark$}
\end{itemize}
}
\sepp

\begin{abstract}
\noindent\emph{\textbf{Abstract}}~ 
Parameterization extends higher-order processes with the capability of abstraction and application (like those in lambda-calculus). As is well-known, this extension is strict, i.e., higher-order processes equipped with parameterization is computationally more expressive. This paper studies higher-order processes with two kinds of parameterization: one on names and the other on processes themselves. We present two main results. One is that in presence of parameterization, higher-order processes can encode first-order (name-passing) processes in a quite neat fashion, in contrast to the fact that higher-order processes without parameterization cannot encode first-order processes at all. We present two such encodings and analyze their properties in depth, particularly full abstraction. In the other result, we provide a simpler characterization of the (standard) context bisimulation for higher-order processes with parameterization, in terms of the normal bisimulation that stems from the well-known normal characterization for higher-order calculus. These results demonstrate more essence of the parameterization method in the higher-order paradigm toward expressiveness and behavioural equivalence.

\vspace*{.1cm}
\noindent\emph{keywords}: Parameterization, Encoding, Context bisimulation, Higher-order, First-order, Processes %, Name-passing, Process-passing,

\vspace*{.1cm}
\noindent\emph{2000 MSC}: 68Q85
\end{abstract}


%----------------------------------------------------------------------------------------------
%\input{scribble.tex}
\input{introduction.tex}
\input{preliminary.tex}
\input{encoding.tex}
\input{encoding_variant.tex}
\input{normal.tex}
\input{conclusion.tex}
%----------------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------------
\sepp
\noindent\textbf{Acknowledgements}\;\;
%This work has been supported by project ANR 12IS02001 PACE and NSF of China (61261130589, 61472239, 61572318). 
We are grateful to the referees of EXPRESS/SOS 2016 for their useful comments on this article and related work. We also thank Qiang Yin for the helpful discussion. 
%Alan Schmitt
\sepp

%-------------------------bibliography------------------------------------------------------------
%\clearpage
%\vspace*{-3mm}
%\nocite{*}
\bibliographystyle{eptcs}
\bibliography{process}
%-----------------------------------------------------------------------------------------------

%-----------------------------------------------------------------------------------------------
%\iftoggle{appendixing}{%
  %using appendixing
\sepp\sepp
%\clearpage
\appendix
\noindent\textbf{\Large Appendix}
%\sepp

\noindent\textit{Remark}. For the sake of conciseness, in the arguments %in the appendix, 
we sometimes omit the existential statement such as ``for some ..." if clear from context.

%\input{appendix_proof_encoding.tex}
\input{appendix_proof_normal.tex}
%\input{appendix_proof_variant_encoding.tex}
%}{%
  %no appendixing
%}

%-----------------------------------------------------------------------------------------------

\end{document}
